---
title: "SEM study 3"
author: "SMK"
date: "`r Sys.Date()`"
output: rmdformats::material
---

# Packages Used
```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(apaTables)
library(gt)
library(sjPlot)
library(rmdformats)
library(psych)
library(lm.beta)
library(BaylorEdPsych)
library(gtsummary)
library(ggplot2)
library(ggthemes)
library(ggcorrplot)
library(extrafont)
library(lavaan)
library(tidySEM)
library(semPlot)
library(RColorBrewer)
library(viridis)
library(reshape2)

```

***
# Dataset
```{r warning=FALSE, message=FALSE}
setwd("C:\\Users\\sarah\\Documents\\PhD\\All data files")
originaldata <- read.csv("Study3AllData.csv",header =TRUE)
```

## Variables
```{r warning=FALSE, message=FALSE}
names(originaldata)
```

## Composite variables
```{r warning=FALSE, message=FALSE}
Filler<-originaldata$F1 + originaldata$F2
SAtotal<-originaldata$SA1 + originaldata$SA2 + originaldata$SA3 + originaldata$SA4
LIplus<-originaldata$LI1 + originaldata$LI2 + originaldata$LI3 + originaldata$LI4 + originaldata$LI5 + originaldata$LI6
LItotal<-originaldata$LI1 + originaldata$LI2 + originaldata$LI3 + originaldata$LI4 + originaldata$LI5
NRtotal<-originaldata$NR1 + originaldata$NR2 + originaldata$NR4 + originaldata$NR5
MTtotal<-originaldata$MT1 + originaldata$MT2 + originaldata$MT3 + originaldata$MT4 + originaldata$MT5 + originaldata$MT6
RMAtotal<-SAtotal+LItotal+NRtotal+MTtotal
alldata<-cbind(originaldata, Filler, SAtotal, LIplus, LItotal, NRtotal, MTtotal, RMAtotal)
```

# Data Cleaning
## Remove cases where duration is less than 4 minutes (240 seconds)
```{r warning=FALSE, message=FALSE}
cleandata <- alldata[!(alldata$Duration< 240),]
```

## Remove cases with over 5% missing data
```{r warning=FALSE, message=FALSE}
cleanerdata<-cleandata
percentmiss<- function(x){sum(is.na(x))/length(x)*100}
missing= apply(cleanerdata, 1, percentmiss)
table(missing)
nomissing<-cleanerdata[missing<5,]
summary(is.na(nomissing))
```
There is still a missing value in Sentence, Filler and Age so Median Value Imputation will be used for this:
```{r}
cleanestdata<-nomissing
medSent<-(median(cleanestdata$Sentence, na.rm = TRUE))
cleanestdata[is.na(cleanestdata$Sentence), "Sentence"]<-medSent
medFiller<-(median(cleanestdata$Filler, na.rm = TRUE))
cleanestdata[is.na(cleanestdata$Filler), "Filler"]<-medFiller
medAge<-(median(cleanestdata$Age, na.rm = TRUE))
cleanestdata[is.na(cleanestdata$Age), "Age"]<-medAge
summary(is.na(cleanestdata))
```
## Remove multivariate outliers 
This analysis will ignore demographic columns (1:17), individual scale and filler items (25:50), LIplus (52) and the RMA composite score (56) for an accurate mahalanobis distance score
```{r warning=FALSE, message=FALSE}
mahal<- mahalanobis(cleanestdata[,c(18:24,51,53,54,55)], colMeans(cleanestdata[,c(18:24,51,53,54,55)],na.rm = TRUE),cov(cleanestdata[,c(18:24,51,53,54,55)], use = "pairwise.complete.obs"))
cutoff<- qchisq(.999,ncol(cleanestdata[,c(18:24,51,53,54,55)]))
cutoff
summary(mahal<cutoff)
```

```{r warning=FALSE, message=FALSE}
nooutliers<-cleanestdata[mahal<cutoff,]
```

## Remove failed attention checks
The filler items act as attention checks in the RMA scale. The items ("This society should devote more effort to preventing rape" and "Victims of rape should be allowed to choose whether they speak with a male or female police officer") are merely statements regarding rape that most people would agree with and thus offer a deviation in response from most other items. However individuals who express strong acceptance of RMA may not agree with these statements and low scores on filler items should not be considered a lack of attention. So, cases where filler scores were outliers and total RMA scores were less than or equal to the mean, were removed.

```{r}
mean(nooutliers$Filler)-3*sd(cleanestdata$Filler)
mean(nooutliers$RMAtotal)
```

```{r}
finaldata<-nooutliers[!(nooutliers$Filler<=6 & nooutliers$RMAtotal<=43),]
```

```{r}
write.csv(finaldata, "finaldata3.csv")
```

## Subset for analysis
```{r warning=FALSE, message=FALSE}
dataset<-finaldata[,c(12:24,51:56)]
data<-finaldata[,c(12,18:24,51:56)]
```
Final dataset has 347 participants.

## Factoring
```{r warning=FALSE, message=FALSE}
dataset$Gender= factor(dataset$Gender,levels = c(1,2,3,4,5,6),labels = c("male","female","trans male", "trans female", "genderqueer", "different identity"))
dataset$Ethnicity= factor(dataset$Ethnicity,levels = c(1:14),labels = c("White Caucasian","White Mexican","White Sephardic Jew", "East Asian", "South Asian", "Middle Eastern", "Native American", "Latino/Hispanic", "Caribbean", "Black British", "African", "Black African American", "Mixed", "Other"))
dataset$Sexuality= factor(dataset$Sexuality,levels = c(1,2,3,4,5),labels = c("heterosexual","bisexual","homosexual", "asexual", "other sexuality"))
dataset$Victim_known= factor(dataset$Victim_known,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know victim","friend or family member victim", "victim themself"))
dataset$False_acc_known= factor(dataset$False_acc_known,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know accused","friend or family member accused", "accused themself"))
dataset$Verdict= factor(dataset$Verdict,levels = c(0,1),labels = c("Not Guilty", "Guilty"))
dataset$Likert_verdict= factor(dataset$Likert_verdict,levels = c(1,2,3,4,5,6,7),labels = c("Completely unlikely", "Moderately unlikely", "Slightly unlikely", "Neither likely nor unlikely", "Slightly likely", "Moderately likely", "Completely likely"))
dataset$Credibility= factor(dataset$Credibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely incredible", "Moderately incredible", "Slightly incredible", "Neither credible nor incredible", "Slightly credible", "Moderately credible", "Completely credible"))
dataset$Responsibility= factor(dataset$Responsibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely unresponsible", "Moderately unresponsible", "Slightly unresponsible", "Neither responsible nor unresponsible", "Slightly responsible", "Moderately responsible", "Completely responsible"))
dataset$Empathy= factor(dataset$Empathy,levels = c(1,2,3,4,5),labels = c("Not at all", "Slightly", "Moderately", "A lot", "Completely"))
```
***
# Descriptive Statistics - Independant variables {.tabset}

```{r}
dataset %>%
  dplyr::select(Gender, Ethnicity, Sexuality, Victim_known, False_acc_known )%>%
  tbl_summary(
    label= list(Gender ~ "Gender",Ethnicity ~ "Ethnicity", Sexuality~ "Sexual Orientation", Victim_known~ "Rape victim known", False_acc_known~ "False accusation known")) %>%
  modify_caption("<div style='text-align: left;font-weight: bold'> Table 1.<br> Demographic Statistics</div>")
```

## Age
```{r warning=FALSE, message=FALSE}
dataset%>%
  summarise(Variable= "Age",
            Mean=mean(Age, na.rm = TRUE),
            Median= median(Age, na.rm = TRUE),
            SD= sd(Age, na.rm = TRUE))
```

## Gender
```{r warning=FALSE}
g<-ggplot(data=dataset, aes(Gender))
g+geom_histogram(stat="Count", aes(fill=as.factor(Gender))) +
  theme_classic(base_size = 12, base_family = "Cambria") + 
  labs( title = "Gender", x = "Gender Identity", y= "Frequency") +
  scale_fill_brewer(palette="Spectral", direction=-1)+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

## Ethnicity 
```{r warning=FALSE, message=FALSE}
e<-ggplot(data=dataset, aes(Ethnicity))
e+geom_bar(stat="Count", aes(fill=as.factor(Ethnicity))) +
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs(title = "Ethnicity", x = "Ethnicity", y= "Frequency" )+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  scale_fill_viridis(discrete = T)
```

## Sexuality
```{r warning=FALSE}
s<-ggplot(data=dataset, aes(Sexuality))
s+ geom_histogram(stat="Count", aes(fill=as.factor(Sexuality))) +
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Sexuality", x = "Sexuality", y= "Frequency" )+
  scale_fill_brewer(palette="RdPu", direction=-1)
```

## Victim known
```{r warning=FALSE}
v<-ggplot(data=dataset, aes(Victim_known))
v+geom_histogram(stat="Count", aes(fill=as.factor(Victim_known))) +
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Victim known", x = "Victim known", y= "Frequency" ) +
   theme(axis.text.x = element_text(angle = 20, hjust=1)) +
  scale_fill_brewer(palette="PRGn")

```

## False Allegations
```{r warning=FALSE}
f<-ggplot(data=dataset, aes(False_acc_known))
f+ geom_histogram(stat="Count",  aes(fill=as.factor(False_acc_known))) +
    theme_classic(base_size = 10,base_family = "Cambria") + 
    labs( title = "False Accusation Known", x = "False Accusation Known", y=  "Frequency" ) +
    theme(axis.text.x = element_text(angle = 20, hjust=1)) +
    scale_fill_brewer(palette="YlGnBu")
```

## Total RMA

```{r warning=FALSE, message=FALSE}
rma<-ggplot(data=dataset, aes(RMAtotal))
rma+geom_histogram(bins = 20, fill= "white", colour="black") + 
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Total Rape Myth Acceptance", x = "Total RMA scores", y= "Frequency" ) + 
  scale_x_continuous(breaks = seq(20, 120, 10))
```

## RMA factor descriptives

```{r}
data %>%
  dplyr::select(SAtotal, MTtotal, NRtotal, LItotal, LIplus, RMAtotal)%>%
  tbl_summary(
    label= list( SAtotal ~ "Total SA", MTtotal ~ "Total MT", NRtotal  ~ "Total NR", LItotal  ~ "Total LI", LIplus ~ "LI plus", RMAtotal  ~ "Total U-IRMA"),
  type= list(all_continuous() ~ "continuous2"),
   digits = all_continuous() ~ 2,
    statistic= all_continuous()~ c("{mean}","{median}","{sd}","{min}, {max}"))%>%       
  modify_caption("<div style='text-align: left;font-weight: bold'> Table 3.<br> U-IRMA Statistics</div>")
```

# Scale Reliability
```{r}
fullscale<- finaldata[,c(25:28, 31:33, 35:39, 41:42, 44:48)]
alpha(fullscale)
```


```{r}
extrascale<-finaldata[, c(25:28, 31:33, 35:39, 41:42, 44:49)]
alpha (extrascale)
```

# Descriptives - Dependant variables {.tabset}

```{r}
describe(data[,3:14], fast=T)
```
## Verdict
```{r}
Ver<-table(dataset$Verdict)
Ver
barplot(Ver, col= grey.colors(2), main = "Verdict")
```

## Likert Verdict
```{r warning=FALSE}
dataset%>%
  dplyr::select(Likert_verdict)%>%
  tbl_summary()

lv<-ggplot(data=dataset, aes(Likert_verdict))
lv+  geom_histogram(stat="Count", aes(fill=as.factor(Likert_verdict))) +
  theme_classic(base_size = 10,base_family = "Cambria") + ylim(c(0,140))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs( title = "Likert Verdict", x = "Likelihood of defendent's guilt", y= "Frequency")+ 
  scale_fill_brewer(palette="RdYlGn")

```

## Confidence
```{r}
co<-ggplot(data=dataset, aes(Confidence))
co+ geom_histogram(bins = 10, fill= "lightseagreen", colour="black")+   
  scale_x_continuous(breaks = seq(0, 100, 10))+ 
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Confidence in Verdict Decisions", x = "% Confidence", y= "Frequency" )
```

## Sentence
```{r}
se<-ggplot(data=dataset, aes(Sentence))
se+ geom_histogram(bins = 10, fill= "olivedrab", colour="black")+   
  scale_x_continuous(breaks = seq(0, 10, 1))+ 
  theme_classic(base_size = 10,base_family = "Cambria") +labs( title = "Sentence Recommendation", x = "Sentence in years", y= "Frequency" )
```

## Credibility
```{r warning=FALSE}
dataset%>%
  dplyr::select(Credibility)%>%
  tbl_summary()

cr<-ggplot(data=dataset, aes(Credibility))
cr+  geom_histogram(stat="Count", aes(fill=as.factor(Credibility))) +
  theme_classic(base_size = 10,base_family = "Cambria") + ylim(c(0,140))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs( title = "Credibility", x = "Credibility Rating", y= "Frequency" )+
  scale_fill_brewer(palette="RdYlGn")
```

## Responsibility
```{r warning=FALSE}
dataset%>%
  dplyr::select(Responsibility)%>%
  tbl_summary()

re<-ggplot(data=dataset, aes(Responsibility))
re+  geom_histogram(stat="Count", aes(fill=as.factor(Responsibility))) +
  theme_classic(base_size = 10,base_family = "Cambria") + ylim(c(0,140))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs(title = "Responsibility", x = "Responsibility rating", y= "Frequency" )+
  scale_fill_brewer(palette="RdYlGn", direction = -1)
```

## Empathy
```{r warning=FALSE, message=FALSE}
dataset%>%
  dplyr::select(Empathy)%>%
  tbl_summary()

em<-ggplot(data=dataset, aes(Empathy))
em+  geom_histogram(stat="Count", aes(fill=as.factor(Empathy))) +
  theme_classic(base_size = 10,base_family = "Cambria") + ylim(c(0,140))+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) + 
  labs(title = "Empathy", x = "Empathy rating", y= "Frequency" ) +
  scale_fill_brewer(palette="RdYlGn")
```

***
# Correlation Matrix {.tabset}
Pearson's correlation coefficients were generated in a matrix in order to explore relationships between all independent and dependent variables.

## Neat Matrix
```{r}
tab_corr(data)
```


## Scatterplot
```{r warning=FALSE, message=FALSE}
corr<-round(cor(data),2)
ggcorrplot(corr,type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle",
           colors= c("deepskyblue4","white","green4"),
           ggtheme=theme_classic (base_family = "Times", base_size = 10)) 
           
```

```{r}
Guiltydata<-data[(data$Verdict==1),]
cor(Guiltydata$Likert_verdict, Guiltydata$Confidence)


Notguiltydata<-data[(data$Verdict==0),]
cor(Notguiltydata$Likert_verdict, Notguiltydata$Confidence)


```


***
# Mean Comparison {.tabset}
3 sets of independent samples t-tests were run to compare differences in the means for all dependent and independent variables based on Verdict decisions and Gender. Eta-squared values are also presented for an effect size; Cohen's(1988) guidelines for interpreting these values are:
.01=small effect, .06=moderate effect, .14=large effect

## Verdict t-tests
```{r}
verttest<-lapply(data[,c(3:13)],function(x)t.test(x~dataset$Verdict,var.eq=F))
vertable<-map_df(verttest, broom::tidy, .id="var")
vertable
print.data.frame(vertable)

tvalues<-vertable$statistic
eta<-function(x){(x*x)/(x*x+(n-1))}
n=347
eta(tvalues)
```
Boxplot
```{r}
datalong<-melt(data[,c(2:9, 11:14)], id.var=c("Verdict"))
box1 <- ggplot(data = datalong, aes(x=variable, y=value, fill=factor(Verdict))) + geom_boxplot()
box1 + facet_wrap( ~ variable, scales="free")+theme_classic(base_size = 10)+  scale_fill_discrete(name = "Verdict", labels = c("Not Guilty", "Guilty"))  

```
## Gender differences
```{r}
Sex<-factor(data$Gender,levels = c(1,2),labels = c( "Male","Female"))
datas<-cbind(data, Sex= as.numeric(Sex))

sexttest<-lapply(data[,c(3:9, 11:14)], function(x)t.test(x~Sex,var.eq=F))
sexttable<-map_df(sexttest,broom::tidy, .id="var")
sexttable
print.data.frame(sexttable)

tvalues2<-sexttable$statistic
eta(tvalues2)
```
Boxplot
```{r}
datalong2<-melt(datas[,c(3:9, 11:15)], id.var=c("Sex"))
box2 <- ggplot(data = datalong2, aes(x=variable, y=value, fill=factor(Sex))) + geom_boxplot()
box2 + facet_wrap( ~ variable, scales="free")+theme_classic(base_size = 10)+  scale_fill_discrete(name = "Gender", labels = c("Male", "Female", "Other Gender"))
```

Chi-square test
```{r warning=FALSE, message=FALSE}
Guilt<-factor(data$Verdict,levels = c(0,1),labels = c("Not Guilty", "Guilty"))
datas<-cbind(datas,Guilt)
chitable<-table(Sex,Guilt)
chisq.test(chitable, correct = T)
barplot(chitable, beside=T, legend=T)
```

***

# Hierarchical regression

```{r warning=FALSE, message=FALSE}
regoutput1=lm(Likert_verdict~Gender+Confidence,data)
summary(regoutput1)
lm.beta(regoutput1)
apa.reg.table(regoutput1)

```

## Step 2
```{r warning=FALSE, message=FALSE}
regoutput2=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal,data)
summary(regoutput2)
lm.beta(regoutput2)
apa.reg.table(regoutput2)
```


## Step 3
```{r warning=FALSE, message=FALSE}
regoutput3=lm(Likert_verdict~Gender+Confidence+SAtotal+NRtotal+LItotal+Credibility+Responsibility+Empathy,data)
summary(regoutput3)
lm.beta(regoutput3)
```

## Regression Model comparison
```{r warning=FALSE, message=FALSE}
anova(regoutput1,regoutput2)
anova(regoutput1,regoutput2,regoutput3)
apa.reg.table(regoutput3)
tbl_regression(regoutput3)
```

# Logistic regression 
```{r warning=FALSE, message=FALSE}
logmodel<-glm(Verdict~ Confidence + Gender + SAtotal + LItotal + NRtotal + Credibility + Responsibility + Empathy, family = binomial(link = logit), data= data)
summary(logmodel)
logmodel%>%
  tbl_regression(exponentiate = TRUE)%>% add_vif()
```

The test below checks whether the change in errors is significantly less for the model without predictors. 
```{r}
options(scipen = 999)
chidiff<-logmodel$null.deviance-logmodel$deviance
dfdiff<-logmodel$df.null-logmodel$df.residual
chidiff
dfdiff
pchisq(chidiff, dfdiff, lower.tail = F)
```

```{r}
PseudoR2(logmodel)
```

```{r}
correct<-logmodel$fitted.values
binarycorrect<-ifelse(correct>0.5,1,0)
binarycorrect<-factor(binarycorrect, levels=c(0,1), labels=c("Not Predicted","Predicted"))
Verdict<-factor(data$Verdict, levels = c(0,1), labels = c("Not Guilty", "Guilty"))
table(data$Verdict, binarycorrect)
```

***
# Mediation Analysis {.tabset}

```{r}
Verdict<-data$Verdict
LItotal<-data$LItotal
Credibility<-data$Credibility
SAtotal<-data$SAtotal
Responsibility<-data$Responsibility
NRtotal<-data$NRtotal
Empathy<-data$Empathy
```

## Credibility
```{r warning=FALSE, message=FALSE}
med1 <- '
    # direct effect
      Verdict ~ c*LItotal
      direct := c
  
    # regressions
      Credibility ~ a*LItotal
      Verdict ~ b*Credibility
  
    # indirect effect (a*b)
      indirect := a*b
  
    # total effect
      total := c + (a*b)
'
credmed <- sem(med1, data = data, ordered = c("Verdict"), se = "bootstrap", bootstrap = 5000, estimator= "DWLS")
```

When the ordered= argument is used, lavaan will automatically switch to the WLSMV estimator but diagonally weighted least squares (DWLS) is used estimate the model parameters. However, it will use the full weight matrix to compute robust standard errors, and a mean- and variance-adjusted test statistic (Rosseel, 2021).

```{r warning=FALSE, message=FALSE}
semPaths(credmed, what="std",whatLabels = "std", sizeMan = 15, sizeInt = 15, sizeLat = 15,edge.label.cex=1.5, rotation=2, style = "lisrel", intercepts = F, residuals = F, nCharNodes=0, fade=F)
```


```{r warning=FALSE, message=FALSE}
summary(credmed, standardize = TRUE, rsquare = TRUE)
parameterestimates(credmed, standardized = TRUE, boot.ci.type = "bca.simple")
```

## Responsibility
```{r warning=FALSE, message=FALSE}
med2 <- '
    # direct effect
      Verdict ~ c*SAtotal
      direct := c
  
    # regressions
      Responsibility ~ a*SAtotal
      Verdict ~ b*Responsibility
  
    # indirect effect (a*b)
      indirect := a*b
  
    # total effect
      total := c + (a*b)
'
respmed <- sem(med2, data = data, ordered = c("Verdict"), se = "bootstrap", bootstrap = 5000, estimator= "DWLS")
```


```{r warning=FALSE, message=FALSE}
semPaths(respmed, what="std",whatLabels = "std", sizeMan = 15, sizeInt = 15, sizeLat = 15,edge.label.cex=1.5, rotation=2, style = "lisrel", intercepts = F, residuals = F, nCharNodes=0)
```

```{r warning=FALSE, message=FALSE}
summary(respmed, standardize = TRUE, rsquare = TRUE)
parameterestimates(respmed, standardized = TRUE, boot.ci.type = "bca.simple")
```

## Empathy
```{r warning=FALSE, message=FALSE}
med3 <- '
    # direct effect
      Verdict ~ c*NRtotal
      direct := c
  
    # regressions
      Empathy ~ a*NRtotal
      Verdict ~ b*Empathy
  
    # indirect effect (a*b)
      indirect := a*b
  
    # total effect
      total := c + (a*b)
'
empmed <- sem(med3, data = data, ordered = c("Verdict"), se = "bootstrap", bootstrap = 5000, estimator= "DWLS")
```


```{r warning=FALSE, message=FALSE}
semPaths(empmed, what="std",whatLabels = "std", sizeMan = 15, sizeInt = 15, sizeLat = 15,edge.label.cex=1.5, rotation=2, style = "lisrel", intercepts = F, residuals = F, nCharNodes=0)
```

```{r warning=FALSE, message=FALSE}
summary(empmed, standardize = TRUE, rsquare = TRUE)
parameterestimates(empmed, standardized = TRUE, boot.ci.type = "bca.simple")

```


***
# CFA

```{r}
LIcfa<-'
LI=~1*LI1+LI2+LI3+LI4+LI5'
LIfit<-cfa(LIcfa, finaldata)
summary(LIfit, fit.measures=T)


```

```{r}
LIcfa2<-'
LI=~1*LI1+LI2+LI3+LI4+LI5+LI6'
LIfit2<-cfa(LIcfa2, finaldata)
summary(LIfit2, fit.measures=T)

```


```{r}
SAcfa<-'
SA=~1*SA1+SA2+SA3+SA4'
SAfit<-cfa(SAcfa, finaldata)
summary(SAfit, fit.measures=T)

```

```{r}
NRcfa<-'
NR=~1*NR1+NR2+NR4'
NRfit<-cfa(NRcfa, finaldata)
summary(NRfit, fit.measures=T)

```

```{r}
CFAmodel<-'
LI=~1*LI1+LI2+LI3+LI4+LI5+LI6
SA=~1*SA1+SA2+SA3+SA4
NR=~1*NR1+NR2+NR4+NR5
SA~~LI+NR
LI~~NR'
CFAfit<-cfa(CFAmodel, finaldata)
summary(CFAfit, fit.measures=T)
modificationindices(CFAfit, sort=T)
```

```{r}
CFAmodel1<-'
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4
NR=~1*NR1+NR2+NR4+NR5
SA~~LI+NR
LI~~NR
'
CFAfit1<-cfa(CFAmodel1, finaldata)
summary(CFAfit1, fit.measures=T)
modificationindices(CFAfit1, sort=T)
```

# SEM
```{r}
semdata <- finaldata %>% 
   mutate(Scaleconf = Confidence / 10)
```


```{r warning=FALSE, message=FALSE}
SEMmodel<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4
NR=~1*NR1+NR2+NR4+NR5


#Regression equations
Verdict~b*Credibility+e*Responsibility+y*Empathy
Verdict~c*LI + f*SA + z*NR
Credibility~Empathy
Credibility~a*LI
Responsibility~d*SA
Empathy~x*NR

#direct & indirect paths
indirectcred := a*b
totalcred := c + (a*b)

indirectresp := d*e
totalresp := f + (d*e)

indirectemp := x*y
totalemp := z + (x*y)

#Estimating endogenous variables covariance
SA~~LI+NR
LI~~NR

'

fitSEMmodel<-sem(SEMmodel, data=semdata, ordered = c("Verdict"))
```


```{r}
set.seed(2021)
summary(fitSEMmodel, fit.measures=TRUE)
parameterestimates(fitSEMmodel,standardized = TRUE, rsquare=TRUE, output="text")
modificationindices(fitSEMmodel, sort=TRUE)
```

## model 1- remove direct paths

```{r}

SEMmodel1<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#regression equations
Verdict~b*Credibility+e*Responsibility+y*Empathy
Credibility~Empathy
Credibility~a*LI
Responsibility~d*SA
Empathy~x*NR


#Indirect pathways
indirectcred := a*b
indirectresp := d*e
indirectemp := x*y


#covariance
SA~~LI+NR
LI~~NR

'
fitSEMmodel1<-sem(SEMmodel1, data=semdata, ordered = c("Verdict"))


set.seed(2021)
summary(fitSEMmodel1, fit.measures=TRUE)
parameterestimates(fitSEMmodel1,standardized = TRUE)
modificationindices(fitSEMmodel1, sort=TRUE)

```


## model 2 - add resp to emp
```{r}
SEMmodel2<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#regression equation
Verdict~b*Credibility+d*Responsibility+f*Empathy
Credibility~ Empathy 
Empathy~ Responsibility
Credibility~a*LI
Responsibility~c*SA
Empathy~e*NR


#Indirect pathways
indirectcred := a*b
indirectresp := c*d
indirectemp := e*f


#Estimating endogenous variables covariance
SA~~LI+NR
LI~~NR

'
fitSEMmodel2<-sem(SEMmodel2, data=semdata, ordered = c("Verdict"))



set.seed(2021)
summary(fitSEMmodel2, fit.measures=TRUE)
parameterestimates(fitSEMmodel2,standardized = TRUE)
modificationindices(fitSEMmodel2, sort=TRUE)

```


## model 3 - alternative add resp to cred
```{r}
SEMmodel3<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5+LI6
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#regression equations
Verdict~b*Credibility+d*Responsibility+f*Empathy
Credibility~Empathy+Responsibility
Credibility~a*LI
Responsibility~c*SA
Empathy~e*NR


#Indirect pathways
indirectcred := a*b
indirectresp := c*d
indirectemp := e*f



#Estimating endogenous variables covariance
SA~~LI+NR
LI~~NR

'

fitSEMmodel3<-sem(SEMmodel3, data=semdata, ordered = c("Verdict"))



set.seed(2021)
summary(fitSEMmodel3, fit.measures=TRUE)
parameterestimates(fitSEMmodel3,standardized = TRUE)
modificationindices(fitSEMmodel3, sort=TRUE)
```


# Measurement Invariance

Configural
```{r}
sex <- ifelse(semdata$Gender == 1, 1, 0)
semdata1<-cbind(semdata, sex)


configmodel<-sem(fitSEMmodel3, data=semdata1, ordered = c("Verdict"), group= "sex", meanstructure = TRUE)
summary(configmodel)
fitMeasures(configmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```


